Analytical Predictions of Exoplanet Obliquities Generated by Planet-Disk Interactions

### 2020-02-24 writeups/Su_disk_disp.tex
stash, I think almost finalized

%TODO
% rework 3->2->1 ??? part, probably also the 3 -> 3 part
% Fig 7 caption lol
    \documentclass[
        fleqn,
        usenatbib,
        % referee,
    ]{mnras}
    \usepackage{
        amsmath,
        amssymb,
        newtxtext,
        newtxmath,
        graphicx,
        ae, aecompl,
        booktabs,
        caption,
        subcaption,
    }
    \usepackage[T1]{fontenc}
    \captionsetup{compatibility=false}

@@

Throughout this paper, we consider $\alpha$ constant, but allow $g$ to vary in
time. In the dispersing disk scenario of \citet{millholland_disk}, $\abs{g}$
decreases in time due to the decreasing disk mass. We consider a simple
exponential decay model
\begin{equation}
    M_{\rm d}(t) = M_{\rm d}(0)e^{-t/t_{\rm d}},\label{eq:dmd_dt}
\end{equation}
with $t_{\rm d}$ constant. This implies $\mathrm{d}\eta / \mathrm{d}t = -\eta /
t_{\rm d}$. In dimensionless units, we have
\begin{equation}
    \rd{\eta}{\tau} = -\epsilon \eta\label{eq:deta_dt},
\end{equation}
where
\begin{align}
    \epsilon \equiv{}& \frac{1}{\alpha t_{\rm d}},\label{eq:eps_def}\\
        ={}& 0.015 \p{\frac{k_{\rm p}}{6k_{\rm qp}}}
            \p{\frac{m_{\rm p}/M_\star}{0.001}}
            \p{\frac{a_{\rm p}}{1\;\mathrm{AU}}}^3\nonumber\\
        &\times \p{\frac{R_{\rm p}}{R_{\rm J}}}^{-3}
            \p{\frac{\Omega_{\rm p}}{2\pi/\p{10\;\mathrm{days}}}}
            \p{\frac{t_{\rm d}}{10\;\mathrm{Myr}}}^{-1}.
\end{align}
Eqs.~\eqref{eq:dsdt_base} and~\eqref{eq:deta_dt} together constitute our system
of study.

@@

Spin states satisfying $\p{\rd{\uv{s}}{t}}_{\rm rot} = 0$ are referred to as
\emph{Cassini States} (CSs). They require that $\uv{s}$, $\uv{l}$, and
$\uv{l}_{\rm d}$ be coplanar. There are either two or four CSs, depending
on the values of $\eta$. They are specified by the obliquity $\theta$ and the
precessional phase of $\uv{s}$ around $\uv{l}$, denoted by $\phi$. Following
the standard convention and nomenclature (see Fig.~\ref{fig:cs_locs}), CSs 1, 3, 4
have $\phi = 0$ and $\theta < 0$, corresponding to $\uv{s}$ and $\uv{l}_{\rm
d}$ being on opposite sides of $\uv{l}$, while CS2 has $\phi = \pi$ and $\theta
> 0$, corresponding to $\uv{s}$ and $\uv{l}_{\rm d}$ being on the same side of
$\uv{l}$. When $\eta < \eta_{\rm c}$, where
\begin{equation}
    \eta_{\rm c} \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{-3/2},\label{eq:etac}
\end{equation}
all four CSs exist, and when $\eta > \eta_{\rm c}$, only CSs 2, 3 exist. The CS
obliquities as a function of $\eta$ are shown in Fig.~\ref{fig:cs_locs}.
\begin{figure*}
    \includegraphics[width=0.45\textwidth]{plots_diskdisp/2_3vec.png}\hfil
    %
    \includegraphics[width=0.45\textwidth]{plots_diskdisp/2_cs_locs.png}
    \caption{Left: Definition of angles in the Cassini state configuration and
    the adopted sign convention for $\theta$. Right: Cassini state obliquities
    as a function of $\eta$ for $I = 5^\circ$, where $\theta \in [-\pi, \pi]$
    is the traditional definition of the polar angle. The vertical dashed line
    indicates $\eta_{\rm c}$ ($= 0.766$ for $I = 5^\circ$), where CS1 and CS4
    merge and annihilate, and the horizontal dashed lines indicate $\theta = I$
    and $I - 180^\circ$, the asymptotic values for CSs 2 and 3 for $\eta \gg
    \eta_{\rm c}$.}\label{fig:cs_locs}
\end{figure*}

@@

As an example, consider a system in zone II in panel (d) of
Fig.~\ref{fig:eq_1contours}. As $\eta decreases, zone II$ will shrink while
zones I and III will expand until the trajectory crosses the separatrix. Suppose
the trajectory exits zone II at some $\eta_\star$, then the probability of the
II $\to$ I transition is $\Pr\p{\rm II \to I} = -\dot{A}_{\rm I} / \dot{A}_{\rm
II}$, while the II $\to$ III transition occurs with probability $\Pr\p{\rm II
\to III} = -\dot{A}_{\rm III} / \dot{A}_{\rm II}$.

@@

        Then, as $\eta$ continues to decrease, a second $\eta_2$ value exists
        for which $A_{\rm m} = A_{\rm II}(\eta_2)$, upon which the trajectory
        is ejected to zone I and $A_f = -A_{\rm I}(\eta_2)$. Note that $\eta_2
        < \eta_{\rm \max, II}$ necessarily, as zone II must be shrinking in
        order for the trajectory to be ejected. The final obliquity is again
        given by Eq.~\eqref{eq:qfaf}.

@@

        Note that a small deviation from $\theta = \theta_{\rm sd, i}$ occurs
        because we use finite $\eta_{\rm i}$, as hinted at in
        Section~\ref{sss:a_evo}. This is because for $\theta_{\rm sd, i}
        \gtrsim \pi/2$, trajectories are better described as librating about
        CS3. Nevertheless, we can still approximate $A_{\rm i}$ to good
        accuracy as the solid angle enclosed by libration about CS3 with polar
        angle $2\pi + \theta_3 - \theta_2 - \theta_{\rm sd, i}$. This recovers
        the correct $\theta_{\rm f}$-$\p{\theta_{\rm sd, i}}$ mapping for the
        III $\to$ III regime, as can be seen visibly in
        Fig.~\ref{fig:3_ensemble_20_35}.
\end{enumerate}
In summary, starting from an initial condition with phase space area $A_{\rm i}$
at $\eta = \eta_{\rm i} \gg 1$, the five evolutionary tracks are:
\begin{enumerate}
    \item $A_{\rm i} \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$. Both the II
        $\to$ III and the II $\to$ I tracks are possible.

@@

    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo21_subplots.png}
    \caption{Fiducial simulation following the II $\to$ I
    track. An initial $\theta_{\rm sd, i} = 0.3\;\mathrm{rad} \approx
    17.2^\circ$ was used, as well as $\epsilon = 3 \times 10^{-4}$. Top plot
    upper panel: plot of $\cos \theta(t)$ (green) in an example simulation.
    Overlaid are the locations of Cassini State 2 (red), and upper and lower
    bounds on the separatrix (black). Note that the trajectory successfully
    tracks CS2 to an obliquity $\theta \approx 90^\circ$. Light vertical blue
    lines denote times portrayed in bottom plot. Top plot lower panel: plot of
    the enclosed separatrix area obtained by integrating the simulated
    trajectory (blue dots) and adiabatic theory (red line). Even though the
    enclosed area jumps at separatrix crossing, the resultant $A$ is still
    accurately predicted. Lower plot: snapshots in the $\p{\cos \theta, \phi}$
    space of the simulation trajectories for the vertical blue lines in the top
    plots. These times correspond to the start of the simulation, the appearance
    of the separatrix, two panels depicting the separatrix crossing process, and
    a final snapshot at $\eta = 10^{-3.5}$. The green line denotes a full
    circulation or libration cycle at the selected time, including an arrow for
    directionality. The separatrix at the start/end of the portrayed cycle are
    shown in solid/dashed black lines respectively. Also labeled is CS2 at the
    start of the cycle (red). Finally, the enclosed phase space area is shaded
    in grey ($A > 0$) and red ($A < 0$).}\label{fig:ad_21}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo23.png}

    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo23_subplots.png}
    \caption{Same as Fig.~\ref{fig:ad_21} but for the II $\to$ III track.
    $\theta_{\rm sd, i} = 0.3\;\mathrm{rad}$ and $\epsilon = 3.01 \times
    10^{-4}$.}\label{fig:ad_23}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo31.png}

@@

    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo321_subplots.png}
    \caption{Same as Fig.~\ref{fig:ad_21} but for the III $\to$ II $\to$ I
    track. $\theta_{\rm sd, i} = 60^\circ$, and $\epsilon = 3.14 \times
    10^{-4}$. Two separatrix crossings are shown.}\label{fig:ad_321}
\end{figure}

@@

In Section~\autoref{s:ad}, we have examined the spin axis evolution in the limit
where $\epsilon \ll 1$ and the evolution is mostly adiabatic (except at
separatrix crossings). We now consider nonadiabatic effects.

@@

We now consider the general problem of how a state evolves when $\eta$ changes
non-adiabatically [i.e.\ $\epsilon \gtrsim \p*{\alpha t_{\rm d}}^{-1}$, see
Eq.~\eqref{eq:ad_constr}]. In Appendix~\ref{s:nonad_app}, we derive a formula
for the final obliquity $\theta_{\rm f}$ assuming no initial spin-disk
misalignment:
\begin{equation}
    \theta_{\rm f}\p{\theta_{\rm sd, i} = 0} = \sqrt{\frac{2\pi}{\epsilon}} \tan
        I\cos I.\label{eq:nonad_q_f}
\end{equation}

@@

To examine stability of each CS, it proves very easy to handle them generally.
We linearize about an equilibrium located at $\phi_{\rm cs} = 0, \pi$ but
arbitrary $\theta_{\rm cs}$. Linearizing Eqs.~\eqref{se:H_eom} about $\phi =
\phi_{\rm cs} + \delta \phi, \theta = \theta_{\rm cs} + \delta \theta$ gives
\begin{subequations}\label{se:H_eom_lin}
    \begin{align}
        \rd{\delta \phi}{t} &= \sin \theta_{\rm cs} \delta \theta
            \mp \eta \frac{\sin I}{\sin^2\theta_{\rm cs}} \delta \theta,\\
        \rd{\delta \theta}{t} &= \pm \eta \sin I \delta \phi.
    \end{align}
\end{subequations}
Note that the positive sign corresponds to $\phi_{\rm cs} = 0$. Eliminating
$\delta \theta$ gives
\begin{align}
    \rtd{\delta \phi}{t} &= \p{\sin \theta_{\rm cs}
        \mp \eta \sin I\csc^2\theta}\p{\pm \eta \sin I} \delta
            \phi,\\
        &\equiv \lambda^2\delta \phi.\label{eq:lambda2}
\end{align}
A plot of $\lambda^2$ for each of the CSs is given in Fig.~\ref{fig:lambda2}.
From the plot, it is clear that only CS4 is a saddle point, while the other
three are centers (stable). The local libration frequency for these points is
just
\begin{align}
    \omega_{\rm lib} &= \sqrt{-\lambda^2},\\
        &= \sqrt{\p{\sin \theta_{\rm cs}
            \mp \eta \sin I \csc^2\theta}\p{\mp \eta \sin I}}.
\end{align}
The libration period is related simply $T_{\rm lib} = \frac{2\pi}{\omega_{\rm
lib}}$.
\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{plots_diskdisp/2_lambdas.png}
    \caption{Plot of $\lambda^2$ per Eq.~\eqref{eq:lambda2} evaluated at each
    of the Cassini States. The vertical axis is rescaled to limit the vertical
    extent of the plot. Note that CS4 is a saddle point ($\lambda^2 > 0$) when
    it exists while all others are centers ($\lambda^2 < 0$). The horizontal
    dashed line is $\lambda^2 = 0$ the instability boundary while $\eta_{\rm c}$ is
    labered in the vertical dashed line.}\label{fig:lambda2}
\end{figure}

@@

We note the resemblance to a similar result given by \citet{malhotra_calc}
describing the impact of a secular resonance sweeping through a system. Both
results have the scaling with repsect to $\epsilon$, despite the vastly
different calculation.

@@

>>>>

%TODO
% Fig 7 caption lol
    \documentclass[
        fleqn,
        usenatbib,
        % referee,
    ]{mnras}
    \usepackage{
        amsmath,
        amssymb,
        newtxtext,
        newtxmath,
        graphicx,
        ae, aecompl,
        booktabs,
        caption,
        subcaption,
    }
    \usepackage[T1]{fontenc}
    \captionsetup{compatibility=false}

@@

Throughout this paper, we consider $\alpha$ constant, but allow $g$ to vary in
time. In the dispersing disk scenario of \citet{millholland_disk}, $\abs{g}$
decreases in time due to the decreasing disk mass. We consider a simple
exponential decay model
\begin{equation}
    M_{\rm d}(t) = M_{\rm d}(0)e^{-t/t_{\rm d}},\label{eq:dmd_dt}
\end{equation}
with $t_{\rm d}$ constant. This implies $\mathrm{d}\eta / \mathrm{d}t = -\eta /
t_{\rm d}$. In dimensionless units, we have
\begin{equation}
    \rd{\eta}{\tau} = -\epsilon \eta\label{eq:deta_dt},
\end{equation}
where
\begin{align}
    \epsilon \equiv{}& \frac{1}{\alpha t_{\rm d}},\nonumber\\
        ={}& 0.015 \p{\frac{k_{\rm p}}{6k_{\rm qp}}}
            \p{\frac{m_{\rm p}/M_\star}{0.001}}
            \p{\frac{a_{\rm p}}{1\;\mathrm{AU}}}^3\nonumber\\
        &\times \p{\frac{R_{\rm p}}{R_{\rm J}}}^{-3}
            \p{\frac{\Omega_{\rm p}}{2\pi/\p{10\;\mathrm{days}}}}
            \p{\frac{t_{\rm d}}{10\;\mathrm{Myr}}}^{-1}.\label{eq:eps_def}
\end{align}
Eqs.~\eqref{eq:dsdt_base} and~\eqref{eq:deta_dt} together constitute our system
of study.

@@

Spin states satisfying $\p{\rd{\uv{s}}{t}}_{\rm rot} = 0$ are referred to as
\emph{Cassini States} (CSs). They require that $\uv{s}$, $\uv{l}$, and
$\uv{l}_{\rm d}$ be coplanar. There are either two or four CSs, depending
on the values of $\eta$. They are specified by the obliquity $\theta$ and the
precessional phase of $\uv{s}$ around $\uv{l}$, denoted by $\phi$. Following
the standard convention and nomenclature (see Figs.~\ref{fig:cs_vecs}
and~\ref{fig:cs_locs}), CSs 1, 3, 4 have $\phi = 0$ and $\theta < 0$,
corresponding to $\uv{s}$ and $\uv{l}_{\rm d}$ being on opposite sides of
$\uv{l}$, while CS2 has $\phi = \pi$ and $\theta > 0$, corresponding to $\uv{s}$
and $\uv{l}_{\rm d}$ being on the same side of $\uv{l}$. When $\eta < \eta_{\rm
c}$, where
\begin{equation}
    \eta_{\rm c} \equiv \p{\sin^{2/3}I + \cos^{2/3}I}^{-3/2},\label{eq:etac}
\end{equation}
all four CSs exist, and when $\eta > \eta_{\rm c}$, only CSs 2, 3 exist. The CS
obliquities as a function of $\eta$ are shown in Fig.~\ref{fig:cs_locs}.
\begin{figure}
    \includegraphics[width=0.45\textwidth]{plots_diskdisp/2_3vec.png}
    \caption{Definition of angles in the Cassini state configuration and the
    adopted sign convention for $\theta$. Traditionally, $\theta \in [-\pi,
    pi]$.}\label{fig:cs_vecs}
\end{figure}
\begin{figure}
    %
    \includegraphics[width=0.45\textwidth]{plots_diskdisp/2_cs_locs.png}
    \caption{Cassini state obliquities as a function of $\eta$ for $I =
    5^\circ$. The vertical dashed line indicates $\eta_{\rm c}$ ($= 0.766$ for
    $I = 5^\circ$), where CS1 and CS4 merge and annihilate, and the horizontal
    dashed lines indicate $\theta = I$ and $I - 180^\circ$, the asymptotic
    values for CSs 2 and 3 for $\eta \gg \eta_{\rm c}$.}\label{fig:cs_locs}
\end{figure}

@@

As an example, consider a system in zone II in panel (d) of
Fig.~\ref{fig:eq_1contours}. As $\eta$ decreases, zone II will shrink while
zones I and III will expand until the trajectory crosses the separatrix. Suppose
the trajectory exits zone II at some $\eta_\star$, then the probability of the
II $\to$ I transition is $\Pr\p{\rm II \to I} = -\dot{A}_{\rm I} / \dot{A}_{\rm
II}$, while the II $\to$ III transition occurs with probability $\Pr\p{\rm II
\to III} = -\dot{A}_{\rm III} / \dot{A}_{\rm II}$.

@@

        Then, as $\eta$ continues to decrease, a second $\eta_2$ value exists
        for which $A_{\rm m} = A_{\rm II}(\eta_2)$, upon which the trajectory
        is ejected to zone I and $A_f = -A_{\rm I}(\eta_2)$. Note that $\eta_2
        < \eta_{\rm \max, II}$ necessarily, as zone II must be shrinking in
        order for the trajectory to be ejected. The final obliquity is finally
        given by Eq.~\eqref{eq:qfaf}.

@@

        Note that for finite $\eta_{\rm i}$, the initial enclosed phase space
        area for III $\to$ III trajectories is not given exactly by using
        $\theta = \theta_{\rm sd, i}$ in Eq.~\eqref{eq:ai_qsd}. This is because
        the initial orbits for these trajectories are better described as
        librating about CS3 with angle of libration $\Delta \theta - \theta_{\rm
        sd, i}$ rather than about CS2 with angle of libration $\theta_{\rm sd,
        i}$. Here, $\Delta \theta$ is the angular distance between CS2 and CS3
        and is not equal to $180^\circ$ except for $\eta_{\rm i} \to \infty$.

        Using such an orbit to evaluate Eq.~\eqref{eq:a_oint} for these initial
        conditions yields the correct enclosed phase space area that predicts
        the $\theta_{\rm f}$-$\p{\theta_{\rm sd, i}}$ mapping for the III $\to$
        III track in the simulation results. This correction is responsible for
        the small cusp at the very right ($\theta_{\rm sd, i} \to 180^\circ$) of
        all of Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
        and~\ref{fig:3_ensemble_20_35}.
\end{enumerate}
In summary, starting from an initial condition with phase space area $A_{\rm i}$
at $\eta = \eta_{\rm i} \gg 1$, the five evolutionary tracks are:
\begin{enumerate}
    \item $A_{\rm i} \in \s{0, A_{\rm II}\p{\eta_{\rm \min, III}}}$. Both the II
        $\to$ III and the II $\to$ I tracks are possible.

@@

    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo21_subplots.png}
    % Even though the enclosed area jumps at
    % separatrix crossing, the resultant $A$ is still accurately predicted.
    \caption{An example of the II $\to$ I evolutionary track for $I = 5^\circ$
    and $\theta_{\rm sd, i} = 17.2^\circ$. Upper panel: The green line shows
    $\cos \theta$ as a function of $\eta$, obtained by numerical integration
    (with $\epsilon = 3 \times 10^{-4}$). Overlaid are the location of Cassini
    State 2 (red) and the upper and lower bounds on the separatrix (black). Note
    that the trajectory tracks CS2 to a final obliquity of $88.57^\circ$. The
    black vertical dashed lines denote instants in the simulation  portrayed in
    bottom panels. Middle panel: The enclosed separatrix area obtained by
    integrating the simulated trajectory (blue dots) and adiabatic theory (red
    line). Lower plot: Snapshots in $\p{\cos \theta, \phi}$ phase space of one
    circulation/libration cycle of the trajectory, shown in dark green with an
    arrow indicating direction. The snapshots correspond to the start of the
    simulation (a), the appearance of the separatrix (b), two panels depicting
    the separatrix crossing process (c-d), and a final snapshot at $\eta =
    10^{-3.5}$ (e). The separatricies at the beginning and end of the portrayed
    orbit in each snapshot are shown in solid/dashed black lines respectively.
    Also labeled is CS2 at the start of each orbit (red point). Finally, the
    enclosed phase space area is shaded in grey ($A > 0$) and red ($A <
    0$).}\label{fig:ad_21}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo23.png}

    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo23_subplots.png}
    \caption{Same as Fig.~\ref{fig:ad_21} but for the II $\to$ III track.
    $\theta_{\rm sd, i} = 17.2^\circ$ and $\epsilon = 3.01 \times
    10^{-4}$.}\label{fig:ad_23}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo31.png}

@@

    \includegraphics[width=0.5\textwidth]{plots_diskdisp/3testo321_subplots.png}
    \caption{Same as Fig.~\ref{fig:ad_21} but for the III $\to$ II $\to$ I
    track. $\theta_{\rm sd, i} = 60^\circ$, and $\epsilon = 3.14 \times
    10^{-4}$. Two separatrix crossings are shown [in panels (c-d) and (e-f)].
    }\label{fig:ad_321}
\end{figure}

@@

In Section~\ref{s:ad}, we have examined the spin axis evolution in the limit
where $\epsilon \ll 1$ and the evolution is mostly adiabatic (except at
separatrix crossings). We now consider nonadiabatic effects.

@@

We now consider the general problem of how a state evolves when $\eta$ changes
non-adiabatically [i.e.\ $\epsilon \gtrsim \p{\alpha t_{\rm d}}^{-1}$, see
Eq.~\eqref{eq:ad_constr}]. In Appendix~\ref{s:nonad_app}, we derive a formula
for the final obliquity $\theta_{\rm f}$ assuming no initial spin-disk
misalignment:
\begin{equation}
    \theta_{\rm f}\p{\theta_{\rm sd, i} = 0} = \sqrt{\frac{2\pi}{\epsilon}} \tan
        I\cos I.\label{eq:nonad_q_f}
\end{equation}

@@

To examine stability of each CS, it proves very easy to handle them generally.
We linearize about an equilibrium located at $\phi_{\rm cs} = 0, \pi$ but
arbitrary $\theta_{\rm cs}$. Linearizing Eqs.~\eqref{se:H_eom} about $\phi =
\phi_{\rm cs} + \delta \phi, \theta = \theta_{\rm cs} + \delta \theta$ gives
\begin{subequations}\label{se:H_eom_lin}
    \begin{align}
        \rd{\delta \phi}{t} &= \sin \theta_{\rm cs} \delta \theta
            \mp \eta \frac{\sin I}{\sin^2\theta_{\rm cs}} \delta \theta,\\
        \rd{\delta \theta}{t} &= \pm \eta \sin I \delta \phi.
    \end{align}
\end{subequations}
Note that the positive sign corresponds to $\phi_{\rm cs} = 0$. Eliminating
$\delta \theta$ gives
\begin{align}
    \rtd{\delta \phi}{t} &= \p{\sin \theta_{\rm cs}
        \mp \eta \sin I\csc^2\theta}\p{\pm \eta \sin I} \delta
            \phi,\\
        &\equiv \lambda^2\delta \phi.\label{eq:lambda2}
\end{align}
A plot of $\lambda^2$ for each of the CSs is given in Fig.~\ref{fig:lambda2}.
From the plot, it is clear that only CS4 is a saddle point, while the other
three are centers (stable). The local libration frequency for these points is
just
\begin{align}
    \omega_{\rm lib} &= \sqrt{-\lambda^2},\\
        &= \sqrt{\p{\sin \theta_{\rm cs}
            \mp \eta \sin I \csc^2\theta}\p{\mp \eta \sin I}}.
\end{align}
The libration period is related simply $T_{\rm lib} = \frac{2\pi}{\omega_{\rm
lib}}$.
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{plots_diskdisp/2_lambdas.png}
    \caption{Plot of $\lambda^2$ per Eq.~\eqref{eq:lambda2} evaluated at each
    of the Cassini States. The vertical axis is rescaled to limit the vertical
    extent of the plot. Note that CS4 is a saddle point ($\lambda^2 > 0$) when
    it exists while all others are centers ($\lambda^2 < 0$). The horizontal
    dashed line is $\lambda^2 = 0$ the instability boundary while $\eta_{\rm c}$ is
    labered in the vertical dashed line.}\label{fig:lambda2}
\end{figure}

@@

@@

We note the resemblance to the well-known eccentricity excitation of an asteroid
sweeping through a secular resonance \citep{malhotra_calc}. Both results have
the same scaling with repsect to the rate of change of secular frequency,
$\epsilon$ in our notation and $\lambda$ in theirs.
